Wigglyhedra

### 2025-01-09 draft/wigglyhedra.tex
increase picture size

We now show that the $\b{g}$-vectors of \cref{def:gvectors} support a polyhedral fan realization of the wiggly complex~$\wigglyComplex_n$ illustrated in \cref{fig:wigglyFan}.
\afterpage{
\begin{figure}
\centerline{\includegraphics[scale=.75]{wigglyFanLabeled}}
\caption{The wiggly fan~$\wigglyFan_2$, intersected with the unit sphere and projected stereographically to the plane. The vertices of the projection are rays of~$\wigglyFan_2$ and are labeled by the corresponding wiggly arcs. Compare with \cref{fig:wigglyComplex}\,(left).}
\label{fig:wigglyFan}
\end{figure}
}

@@

We now construct the wigglyhedron illustrated in \cref{fig:wigglyhedron} when~${n = 2}$.
%
\afterpage{
\begin{figure}
%\centerline{\input{wigglyhedron}}
\centerline{\includegraphics[scale=.75]{wigglyhedron}}
\caption{The wigglyhedron~$\wigglyhedron_2$. The vertices are labeled by the corresponding wiggly pseudotriangulations. Compare to \cref{fig:wigglyComplex}\,(right) and \cref{fig:wigglyLattice}\,(left).}
\label{fig:wigglyhedron}
\end{figure}
}

@@

  We have four possible combinations:
  \begin{enumerate}
  \item \(i' = j\) is an endpoint such that \(\alpha\) travels left starting at \(i'\), and \(i' = j\) is an endpoint such that \(\alpha\) travels right starting at \(j\);
  \item \(i' = j\) is an endpoint such that \(\alpha\) travels left starting at \(i'\), and \(\alpha\) loops around the left of the point \(j\);
  \item \(\alpha\) loops around the right of the point \(i' = j\), and \(i' = j\) is an endpoint such that \(\alpha\) travels right starting at \(j\); 
  \item \(\alpha\) loops around the right of the point \(i' = j\), and \(\alpha\) loops around the left of the point \(j\).
  \end{enumerate}
  It is clear that none of these possibilities can occur within the curve \(\alpha\), and hence \(\beta\) and \(\beta'\) must be pointed.
  Therefore \(T = \{\alpha_1, \ldots, \alpha_k\}\) is a subset of a wiggly pseudotriangulation.

>>>>

We now show that the $\b{g}$-vectors of \cref{def:gvectors} support a polyhedral fan realization of the wiggly complex~$\wigglyComplex_n$ illustrated in \cref{fig:wigglyFan} when~$n = 2$.
\afterpage{
\begin{figure}
\centerline{\includegraphics[scale=1.1]{wigglyFanLabeled}}
\caption{The wiggly fan~$\wigglyFan_2$, intersected with the unit sphere and projected stereographically to the plane. The vertices of the projection are rays of~$\wigglyFan_2$ and are labeled by the corresponding wiggly arcs. Compare with \cref{fig:wigglyComplex}\,(left).}
\label{fig:wigglyFan}
\end{figure}
}

@@

We now construct the wigglyhedron illustrated in \cref{fig:wigglyhedron} when~${n = 2}$.
%
\afterpage{
\begin{figure}
%\centerline{\input{wigglyhedron}}
\centerline{\includegraphics[scale=1.1]{wigglyhedron}}
\caption{The wigglyhedron~$\wigglyhedron_2$. The vertices are labeled by the corresponding wiggly pseudotriangulations. Compare to \cref{fig:wigglyComplex}\,(right) and \cref{fig:wigglyLattice}\,(left).}
\label{fig:wigglyhedron}
\end{figure}
}

@@

\pagebreak
  We have four possible combinations:
  \begin{enumerate}
  \item \(i' = j\) is an endpoint such that \(\alpha\) travels left starting at \(i'\), and \(i' = j\) is an endpoint such that \(\alpha\) travels right starting at \(j\);
  \item \(i' = j\) is an endpoint such that \(\alpha\) travels left starting at \(i'\), and \(\alpha\) loops around the left of the point \(j\);
  \item \(\alpha\) loops around the right of the point \(i' = j\), and \(i' = j\) is an endpoint such that \(\alpha\) travels right starting at \(j\); 
  \item \(\alpha\) loops around the right of the point \(i' = j\), and \(\alpha\) loops around the left of the point \(j\).
  \end{enumerate}
  It is clear that none of these possibilities can occur within the curve \(\alpha\), and hence \(\beta\) and \(\beta'\) must be pointed.
  Therefore \(T = \{\alpha_1, \ldots, \alpha_k\}\) is a subset of a wiggly pseudotriangulation.
